### 2018-06-26 tex/manuscript.tex
added gitignore folder

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{gensymb}
\usepackage{textgreek}
\usepackage{xcolor}
\usepackage[colorlinks]{hyperref}
	\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!60!black},
	urlcolor={blue!40!black}
	}
\usepackage{cleveref}

@@

%4 sections of results ideally, nobody really uses subsections, 6 display items max.
	\section{Microstructure}\label{sec:microstructure} 
		Display 1: Pictures of heads, macrofiber arrangement, and exo-endo ratio at base and apex, across species.
		Explain how everything is laid out across the length of the rostrum, emphasizing that this is key to predicting and understanding the mechanical behavior of the snout during bending.
		No change in total thickness, only relative layer thickness,
		No

>>>>

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{gensymb}
\usepackage{textgreek}
\usepackage{xcolor}
\usepackage[colorlinks]{hyperref}
	\hypersetup{colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!60!black},
	urlcolor={blue!40!black}
	}
\usepackage{cleveref}

@@

%4 sections of results ideally, nobody really uses subsections, 6 display items max.
	\section{Microstructure}\label{sec:microstructure} 
		Display 1: Pictures of heads, macrofiber arrangement, and exo-endo ratio at base and apex, across species.
		Explain how everything is laid out across the length of the rostrum, emphasizing that this is key to predicting and understanding the mechanical behavior of the snout during bending.
		No change in total thickness, only relative layer thickness,
		No resilin either.
